---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

# Count number of examples
n_examples <- length(dir("inst/plumber"))
```

# plumberExamples

This package provides a collection of example APIs built in R using the [Plumber](https://rplumber.io) package.

These examples are meant to highlight common patterns and best practices. They can be used as compelling starting points when getting started with Plumber.

## Installation

You can install the development version of plumberExamples from GitHub with:

```{r, eval=FALSE}
remotes::install_github("sol-eng/plumberExamples")
```

## Usage

There are two main uses cases for this package: running example APIs and examining their source code.

Example APIs can be run using the `plumb_api()` function:
```{r, eval = FALSE}
library(plumber)
plumb_api(package = "plumberExamples", name = "00-hello") %>%
  pr_run()
```

To view the source code associated with the API, add `edit = TRUE` to the function call:
```{r, eval = FALSE}
plumb_api(package = "plumberExamples", name = "00-hello", edit = TRUE)
```

## Examples
There are currently `r n_examples` examples in this package. Each example is located in [`/inst/plumber`](inst/plumber) and can be accessed using the previously described `plumb_api()` function:

```{r, echo = FALSE, results='asis'}
knitr::kable(data.frame(
  Example = list.dirs("inst/plumber", full.names = FALSE, recursive = FALSE),
  Path = paste0("[", 
                list.dirs("inst/plumber", full.names = TRUE, recursive = FALSE),
                "](",
                list.dirs("inst/plumber", full.names = TRUE, recursive = FALSE),
                ")"
  )
))
```

